Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-20 papers/thesis-kirstie/thesis.tex
switch to beavtex for thesis-kirstie

\documentclass[12pt]{article}
\usepackage{setspace}
\doublespacing
%\usepackage[top=1.2in, bottom=1.2in]{geometry}
%\usepackage[top=1.5in]{geometry}
\usepackage[bottom=1.2in]{geometry}
\usepackage{fancyhdr}
\usepackage{yhmath}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\thepage}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{color}
\usepackage{enumitem}
\title{Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory}
\author{Kirstie L. Finster}
\date{August 2020}
\begin{document}
   \maketitle
   \thispagestyle{fancy}

\noindent I. Introduction

@@

Schmidt applied his Soft Fundamental Measure Theory to various fluids with soft repulsive 
and soft attractive potentials, and developed an erf model for 
spheres with steep, short-range soft repulsive potentials~\cite{schmidt2000fluid}. In this paper, 
Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]
\newline
\newline
\noindent IIA. Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)

@@

The WCA potential is not well suited for implementing Density Functional Theory.  Therefore, an erf potential which closely approximates the WCA potential at temperatures of interest will be used instead of the WCA potential. The erf potential is given by 
\begin{equation}
	{V_{erf}=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}
\end{equation} 
where the parameter $\alpha$ is derived by setting the erf potential equal to the WCA potentail when r equals $\alpha$ 
\begin{displaymath}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{displaymath} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
The parameter $\Xi$ is derived by matching the slope of the erf potential to the slope of the WCA potential at r=$\alpha$:
\begin{displaymath}{\frac{dV_{erf}(r=\alpha)}{dr}=\frac{dV_{WCA}(r=\alpha)}{dr}}\end{displaymath} 
and is given by: 
\begin{equation}
	{\Xi=\frac{\alpha}{6\sqrt{\pi}\left(\sqrt{\frac{\epsilon}{k_BT}\ln(2)}+\ln(2)\right)}}
\end{equation}

@@

The Liquid (homogeneous) excess free energy $hF_{excess}$ is computed analytically for a given $n^*$ and $t^*$ using SFMT with a uniform number density profile that does not depend on $\vec r$. 
%done in hf.energy() note- does not depend on fv or gw but does use SFMT):
\begin{displaymath}{\frac{hF_{excess}}{V} = k_BT(\Phi_1+\Phi_2+\Phi_3)}\end{displaymath} 
For the case of a homogeneous number density n, $\Phi_1$, $\Phi_2$, and $\Phi_3$ simplify to:
\begin{displaymath}{\Phi_1= -n_0\ln(1-n_3)}\end{displaymath} 
\begin{displaymath}{\Phi_2= \frac{n_1n_2}{1-n_3}}\end{displaymath} 
\color{red}\begin{displaymath}{\Phi_3=\frac{n_2^3}{24\pi(1-n_3)^2}}\end{displaymath}\color{black}
where \begin{displaymath}{n_i=nw_i}\end{displaymath} 
%\begin{displaymath}{n_0=nw_0}\end{displaymath} 
%\begin{displaymath}{n_1=nw_1}\end{displaymath}
%\begin{displaymath}{n_2=nw_2}\end{displaymath}
%\begin{displaymath}{n_3=nw_3}\end{displaymath}
and the weights are as usual 
\begin{equation}{w_{0}=\frac{w_{2}}{4\pi{r}^2}}\end{equation}
\begin{equation}{w_{1}=\frac{w_{2}}{4\pi{r}}}\end{equation}
\begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation}
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]\end{equation} 
%\begin{displaymath}{w_0=?}\end{displaymath} 
%\begin{displaymath}{w_1=\frac{\alpha}{2}}\end{displaymath}
%\begin{displaymath}{w_2=6.2...\Xi^2 + \pi\alpha^2}\end{displaymath}
%\begin{displaymath}{w_3=\alpha(\pi\Xi^2 + 0.52...\alpha^2)}\end{displaymath} \[\]
\[\]

The Crystal ideal free energy $cF_{ideal}$ is computed in two different ways from the equation 
\begin{displaymath}{F_{ideal}[n(\vec{r})]= k_BT\int[n(\vec{r})\ln(n(\vec{r})\Lambda^3)-n(\vec{r})]dV}\end{displaymath}
with the varying number density profile given by 
\begin{displaymath}{n(|\vec{r}-\vec{R_i}|)=\sum_i{(1-f_v)\frac{\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}}\end{displaymath}
\newline $\bullet$ For small gw values it is assumed that the Guassians do not overlap, in which case the equation for the free energy can be simplified and solved analytically with the result
\begin{displaymath}{cF_{ideal}=(1-f_v)k_BT\left(\ln((1-f_v)\Lambda^3)-3\ln(\sqrt{2\pi{gw}})-\frac{5.0}{2}\right)}\end{displaymath}

%\begin{displaymath}{cF_{ideal}=(1-f_v)k_BT\left(\ln(\frac{(1-fv)2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-3\ln(\sqrt{2\pi{gw}})-\frac{5.0}{2}\right)-DELETE-EQN!}\end{displaymath}

$\bullet$ For larger gw values it is assumed that the Gaussians do overlap, and so the free energy is caluculated computationally. First dx is scaled by gw
\begin{displaymath}{dx_{scaled}=(dx_{input})(gw)}\end{displaymath}
then $n(\vec{r})$ is computed at one position of $\vec{r}$ within the primitive cell taking into account the contribution of Gaussians from many (5x5x5) nearby cells whose centers are given by $R_i$.
%\begin{displaymath}{n(|\vec{r}-\vec{R_i}|)+=\frac{(1-f_v)\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}\end{displaymath}
The contribution to the free energy of $n(\vec{r})$ at the one position is then added to the accumulating sum.
%\begin{displaymath}{cF_{ideal}+=k_BTn(ln(\frac{(n)2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)dV-DELETE-EQN!}\end{displaymath}
%\begin{displaymath}{cF_{ideal}+=k_BTn(\ln(n\Lambda^3)-1.0)dV}\end{displaymath}
This process is repeated for all positions within one primitive cell to get the crystal ideal free energy for the primitive cell. This energy is then divided by the volume of the primitive cell to get the crystal ideal free energy per volume.
%\[\]

@@

APPENDIX
\begin{enumerate}

@@

\textbf{1a. Fourier Transform of Weight Function $w_0(r)$:}
\begin{equation}{w_0(r)=\frac{w_2(r)}{4{\pi}r^2}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_0(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r^2}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}
%\[{}\]
\begin{equation}{\widetilde{w}_0(\vec{k})=\int_{0}^{\infty}\int_{-1}^{1}\int_{0}^{2\pi}w_0(r)e^{-i\vec{k}\cdot{\vec{r}}}r^2d{r}d{\cos\theta}d{\phi}}\end{equation}
Set $\vec{k}$ in the direction of $\hat{z}$ 
\begin{equation}{\widetilde{w}_0(k)=\int_{0}^{\infty}\int_{-1}^{1}\int_{0}^{2\pi}w_0(r)e^{-ikr\cos\theta}r^2d{r}d{\cos\theta}d{\phi}}\end{equation}
\[{}\]
Calculate $\widetilde{w}_0(k)$ 
\begin{equation}{\widetilde{w}_0(k)=\frac{1}{4{\pi}\sqrt{\pi}a}\int_{0}^{\infty}\left(\frac{1}{r^2}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}r^2\left[\int_{-1}^{1}e^{-ikr\cos\theta}d{\cos\theta}\left(\int_{0}^{2\pi}d{\phi}\right)\right]d{r}}\end{equation}
\[{}\]
\begin{equation}{\widetilde{w}_0(k)=\frac{2\pi}{4{\pi}\sqrt{\pi}a}\int_{0}^{\infty}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\left(\int_{-1}^{1}e^{-ikr\cos\theta}d{\cos\theta}\right)d{r}}\end{equation}
\[{}\]
Set the lower limit to $-\infty$  since the integrand is nearly zero by the time r is zero. 
\begin{equation}{\widetilde{w}_0(k)=\frac{1}{\sqrt{\pi}ka}\int_{-\infty}^{\infty}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\frac{\sin(kr)}{r}d{r}}\end{equation}
\[{}\]
\begin{equation}{\widetilde{w}_0(k)=\frac{\sqrt{\pi}}{2ka}e^{-\left(\frac{\alpha}{2a}\right)^2}\left[\operatorname{erf}\left(\frac{ka}{2}+i\frac{\alpha}{2a}\right)+\operatorname{erf}\left(\frac{ka}{2}-i\frac{\alpha}{2a}\right)\right]}\end{equation}
\[{}\] 
Putting in $a=\frac{\Xi}{\sqrt{2}}$ the final equation for $\widetilde{w}_0(k)$ becomes
\begin{equation}{\widetilde{w}_0(k)=\frac{\sqrt{\pi}}{\sqrt{2}k\Xi}e^{-\left(\frac{\alpha^2}{2\Xi^2}\right)}\left[\operatorname{erf}\left(\frac{k\Xi}{2\sqrt{2}}+i\frac{\alpha}{\sqrt{2}\Xi}\right)+\operatorname{erf}\left(\frac{k\Xi}{2\sqrt{2}}-i\frac{\alpha}{\sqrt{2}\Xi}\right)\right]}\end{equation}

\[{}\]
%\[{}\]
\textbf{1b. Fourier Transform of Weight Function $w_{1}(r)$:}
\begin{equation}{w_1(r)=\frac{w_2(r)}{4{\pi}r}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_1(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\textbf{1c. Fourier Transform of Weight Function $w_{2}(r)$:}
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_2(r)=\frac{1}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\textbf{1d. Fourier Transform of Weight Function $w_{3}(r)$:}
\begin{equation}{w_3(r)=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_3(r)=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{a}\right)\right]}\end{equation}

@@

\begin{equation}{\widetilde{w}_3(k)=\frac{2\pi}{k}\left[\left(1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{a}\right)\right)\left(\frac{\sin(kr)-kr\cos(kr)}{k^2}\right)\bigg|^{\infty}_0\color{white}\right]}\end{equation} \color{black}
\begin{displaymath}{-\int_{0}^{\infty}\left(\frac{\sin(kr)-kr\cos(kr)}{k^2}\right)\left(\frac{2}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\right)d{r}}\end{displaymath}
Evaluating the integral by doing a u-substitution with $u=\frac{r-\frac{\alpha}{2}}{a}$, and setting the lower limit to $-\infty$  since the integrand is nearly zero by the time r is zero this becomes
\begin{equation}{\widetilde{w}_3(k)=\frac{4\pi}{k^3}e^{-\frac{k^2a^2}{4}}\left[\left(1+\frac{k^2a^2}{2}\right)\sin\left(\frac{k\alpha}{2}\right)-\frac{k\alpha}{2}\cos\left(\frac{k\alpha}{2}\right)\right]}\end{equation}
Putting $a=\frac{\Xi}{\sqrt{2}}$ back in, the final equation for $\widetilde{w}_3(k)$ becomes
\begin{equation}{\widetilde{w}_3(k)=\frac{4\pi}{k^3}e^{-\frac{k^2\Xi^2}{8}}\left[\left(1+\frac{k^2\Xi^2}{4}\right)\sin\left(\frac{k\alpha}{2}\right)-\frac{k\alpha}{2}\cos\left(\frac{k\alpha}{2}\right)\right]}\end{equation}

\[{}\]
%\[{}\]
\textbf{2a. Fourier Transform of Vector Weight Function $\vec{w}_{1}(r)$:}
\begin{equation}{\vec{w}_1(\vec{r})=w_1(r)\frac{\vec{r}}{r}}\end{equation}
where
\begin{equation}{w_1(r)=\frac{w_2(r)}{4{\pi}r}}\end{equation}
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_1(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\textbf{2b. Fourier Transform of Vector Weight Function $\vec{w}_{2}(r)$:}
\begin{equation}{\vec{w}_2(\vec{r})=w_2(r)\frac{\vec{r}}{r}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_2(r)=\frac{1}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\begin{equation}{\widetilde{\vec{w}}_2(\vec{k})=\frac{-4\sqrt{\pi}i}{ak}\left[\frac{a\alpha\sqrt{\pi}}{2}e^{-\frac{k^2a^2}{4}}\cos\left(\frac{k\alpha}{2}\right)-\frac{a^3k\sqrt{\pi}}{2}e^{-\frac{k^2a^2}{4}}\sin\left(\frac{k\alpha}{2}\right)\right]}\end{equation} 
\begin{displaymath}{+{~~}\frac{4\sqrt{\pi}i}{ak^2}\left[a\sqrt{\pi}e^{-\frac{k^2a^2}{4}}\sin\left(\frac{k\alpha}{2}\right)\right]{~~}\hat{z}'}\end{displaymath}

>>>>

\documentclass[double,12pt]{beavtex}
\usepackage{graphicx}
\usepackage{rotating} %Package added to allow the rotation of figures and chart on a page, {sidewaysfigure} command
\usepackage{tablefootnote} %Packaged added to allow footnotes in the tabular environment, use \tablefootnote command
\title{Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory}
\author{Kirstie L. Finster}
\degree{Master of Science}
\doctype{Thesis}
\department{Physics}
\depttype{Department}
\depthead{Head}
\major{Physics}
\advisor{David Roundy}
\submitdate{October ??, 2020}
\commencementyear{2020}

\usepackage{color}
\usepackage{amsmath}
\usepackage{subcaption}

\date{August 2020}

\abstract{
  This is a test
}

\begin{document}
   \maketitle
   \mainmatter

\chapter{Introduction}

@@

Schmidt applied his Soft Fundamental Measure Theory to various fluids with soft repulsive 
and soft attractive potentials, and developed an erf model for 
spheres with steep, short-range soft repulsive potentials~\cite{schmidt2000fluid}. In this paper, 
Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]

\section{Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)}

\subsection{Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)}

@@

The WCA potential is not well suited for implementing Density Functional Theory.  Therefore, an erf potential which closely approximates the WCA potential at temperatures of interest will be used instead of the WCA potential. The erf potential is given by 
\begin{equation}
	{V_{erf}=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}
\end{equation} 
where the parameter $\alpha$ is derived by setting the erf potential equal to the WCA potential when r equals $\alpha$ 
\begin{displaymath}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{displaymath} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
The parameter $\Xi$ is derived by matching the slope of the erf potential to the slope of the WCA potential at r=$\alpha$:
\begin{displaymath}{\frac{dV_{erf}(r=\alpha)}{dr}=\frac{dV_{WCA}(r=\alpha)}{dr}}\end{displaymath} 
and is given by: 
\begin{equation}
	{\Xi=\frac{\alpha}{6\sqrt{\pi}\left(\sqrt{\frac{\epsilon}{k_BT}\ln(2)}+\ln(2)\right)}}
\end{equation}

@@

The Liquid (homogeneous) excess free energy $hF_{excess}$ is computed analytically for a given $n^*$ and $t^*$ using SFMT with a uniform number density profile that does not depend on $\vec r$. 
%done in hf.energy() note- does not depend on fv or gw but does use SFMT):
\begin{displaymath}{\frac{hF_{excess}}{V} = k_BT(\Phi_1+\Phi_2+\Phi_3)}\end{displaymath} 
For the case of a homogeneous number density n, $\Phi_1$, $\Phi_2$, and $\Phi_3$ simplify to:
\begin{displaymath}{\Phi_1= -n_0\ln(1-n_3)}\end{displaymath} 
\begin{displaymath}{\Phi_2= \frac{n_1n_2}{1-n_3}}\end{displaymath} 
\color{red}\begin{displaymath}{\Phi_3=\frac{n_2^3}{24\pi(1-n_3)^2}}\end{displaymath}\color{black}
where \begin{displaymath}{n_i=nw_i}\end{displaymath} 
%\begin{displaymath}{n_0=nw_0}\end{displaymath} 
%\begin{displaymath}{n_1=nw_1}\end{displaymath}
%\begin{displaymath}{n_2=nw_2}\end{displaymath}
%\begin{displaymath}{n_3=nw_3}\end{displaymath}
and the weights are as usual 
\begin{align}
  w_{0}(r) &=\frac{w_{2}}{4\pi{r}^2} \\
  w_{1}(r) &=\frac{w_{2}}{4\pi{r}} \\
  w_2(r)&=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2}
  \\
  w_3(r)&=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]
\end{align}
%\begin{displaymath}{w_0=?}\end{displaymath} 
%\begin{displaymath}{w_1=\frac{\alpha}{2}}\end{displaymath}
%\begin{displaymath}{w_2=6.2...\Xi^2 + \pi\alpha^2}\end{displaymath}
%\begin{displaymath}{w_3=\alpha(\pi\Xi^2 + 0.52...\alpha^2)}\end{displaymath} \[\]

The Crystal ideal free energy $cF_{ideal}$ is computed in two different ways from the equation 
\begin{displaymath}{F_{ideal}[n(\vec{r})]= k_BT\int[n(\vec{r})\ln(n(\vec{r})\Lambda^3)-n(\vec{r})]dV}\end{displaymath}
with the varying number density profile given by 
\begin{displaymath}
  {n(|\vec{r}-\vec{R_i}|)=\sum_i{(1-f_v)\frac{\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}}
\end{displaymath}
\begin{itemize}
  \item For small gw values it is assumed that the Guassians do not overlap, in
  which case the equation for the free energy can be simplified and solved
  analytically with the result
  \begin{align}
    cF_{ideal}=(1-f_v)k_BT\left(\ln((1-f_v)\Lambda^3)-3\ln(\sqrt{2\pi{gw}})-\frac{5.0}{2}\right)
  \end{align}
\item For larger gw values it is assumed that the Gaussians do overlap, and so the free energy is caluculated computationally. First dx is scaled by gw
\begin{align}
  dx_{scaled} &= (dx_{input})(gw)
\end{align}
then $n(\vec{r})$ is computed at one position of $\vec{r}$ within the primitive cell taking into account the contribution of Gaussians from many (5x5x5) nearby cells whose centers are given by $R_i$.
%\begin{displaymath}{n(|\vec{r}-\vec{R_i}|)+=\frac{(1-f_v)\exp^{-\frac{{|\vec{r}-\vec{R_i}|}^2}{2{(gw)}^2}}}{\left(\sqrt{2\pi}gw\right)^3}}\end{displaymath}
The contribution to the free energy of $n(\vec{r})$ at the one position is then
added to the accumulating sum.
%\begin{displaymath}{cF_{ideal}+=k_BTn(ln(\frac{(n)2.646476976618268x10^{-6}}{\sqrt{(k_BT)^3}})-1.0)dV-DELETE-EQN!}\end{displaymath}
%\begin{displaymath}{cF_{ideal}+=k_BTn(\ln(n\Lambda^3)-1.0)dV}\end{displaymath}
This process is repeated for all positions within one primitive cell to get the
crystal ideal free energy for the primitive cell. This energy is then divided by
the volume of the primitive cell to get the crystal ideal free energy per
volume.
%\[\]
\end{itemize}

@@

\backmatter

\chapter{Appendix}
\begin{enumerate}

@@

\section{Fourier Transform of Weight Function $w_0(r)$:}
\begin{equation}{w_0(r)=\frac{w_2(r)}{4{\pi}r^2}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_0(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r^2}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}
%\[{}\]
\begin{equation}{\widetilde{w}_0(\vec{k})=\int_{0}^{\infty}\int_{-1}^{1}\int_{0}^{2\pi}w_0(r)e^{-i\vec{k}\cdot{\vec{r}}}r^2d{r}d{\cos\theta}d{\phi}}\end{equation}
Set $\vec{k}$ in the direction of $\hat{z}$ 
\begin{equation}{\widetilde{w}_0(k)=\int_{0}^{\infty}\int_{-1}^{1}\int_{0}^{2\pi}w_0(r)e^{-ikr\cos\theta}r^2d{r}d{\cos\theta}d{\phi}}\end{equation}
\[{}\]
Calculate $\widetilde{w}_0(k)$ 
\begin{equation}{\widetilde{w}_0(k)=\frac{1}{4{\pi}\sqrt{\pi}a}\int_{0}^{\infty}\left(\frac{1}{r^2}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}r^2\left[\int_{-1}^{1}e^{-ikr\cos\theta}d{\cos\theta}\left(\int_{0}^{2\pi}d{\phi}\right)\right]d{r}}\end{equation}
\[{}\]
\begin{equation}{\widetilde{w}_0(k)=\frac{2\pi}{4{\pi}\sqrt{\pi}a}\int_{0}^{\infty}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\left(\int_{-1}^{1}e^{-ikr\cos\theta}d{\cos\theta}\right)d{r}}\end{equation}
\[{}\]
Set the lower limit to $-\infty$  since the integrand is nearly zero by the time r is zero. 
\begin{equation}{\widetilde{w}_0(k)=\frac{1}{\sqrt{\pi}ka}\int_{-\infty}^{\infty}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\frac{\sin(kr)}{r}d{r}}\end{equation}
\[{}\]
\begin{equation}{\widetilde{w}_0(k)=\frac{\sqrt{\pi}}{2ka}e^{-\left(\frac{\alpha}{2a}\right)^2}\left[\operatorname{erf}\left(\frac{ka}{2}+i\frac{\alpha}{2a}\right)+\operatorname{erf}\left(\frac{ka}{2}-i\frac{\alpha}{2a}\right)\right]}\end{equation}
\[{}\] 
Putting in $a=\frac{\Xi}{\sqrt{2}}$ the final equation for $\widetilde{w}_0(k)$ becomes
\begin{equation}{\widetilde{w}_0(k)=\frac{\sqrt{\pi}}{\sqrt{2}k\Xi}e^{-\left(\frac{\alpha^2}{2\Xi^2}\right)}\left[\operatorname{erf}\left(\frac{k\Xi}{2\sqrt{2}}+i\frac{\alpha}{\sqrt{2}\Xi}\right)+\operatorname{erf}\left(\frac{k\Xi}{2\sqrt{2}}-i\frac{\alpha}{\sqrt{2}\Xi}\right)\right]}\end{equation}

\[{}\]
%\[{}\]
\section{Fourier Transform of Weight Function $w_{1}(r)$:}
\begin{equation}{w_1(r)=\frac{w_2(r)}{4{\pi}r}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_1(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\section{Fourier Transform of Weight Function $w_{2}(r)$:}
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_2(r)=\frac{1}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\section{Fourier Transform of Weight Function $w_{3}(r)$:}
\begin{equation}{w_3(r)=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)\right]}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_3(r)=\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{a}\right)\right]}\end{equation}

@@

\begin{multline}
  \widetilde{w}_3(k)=\frac{2\pi}{k}\Bigg[\left(1-\operatorname{erf}\left(\frac{r-\frac{\alpha}{2}}{a}\right)\right)\left(\frac{\sin(kr)-kr\cos(kr)}{k^2}\right)\bigg|^{\infty}_0
   \\
  -\int_{0}^{\infty}\left(\frac{\sin(kr)-kr\cos(kr)}{k^2}\right)\left(\frac{2}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}\right)dr\Bigg]
\end{multline}
Evaluating the integral by doing a u-substitution with $u=\frac{r-\frac{\alpha}{2}}{a}$, and setting the lower limit to $-\infty$  since the integrand is nearly zero by the time r is zero this becomes
\begin{equation}{\widetilde{w}_3(k)=\frac{4\pi}{k^3}e^{-\frac{k^2a^2}{4}}\left[\left(1+\frac{k^2a^2}{2}\right)\sin\left(\frac{k\alpha}{2}\right)-\frac{k\alpha}{2}\cos\left(\frac{k\alpha}{2}\right)\right]}\end{equation}
Putting $a=\frac{\Xi}{\sqrt{2}}$ back in, the final equation for $\widetilde{w}_3(k)$ becomes
\begin{equation}{\widetilde{w}_3(k)=\frac{4\pi}{k^3}e^{-\frac{k^2\Xi^2}{8}}\left[\left(1+\frac{k^2\Xi^2}{4}\right)\sin\left(\frac{k\alpha}{2}\right)-\frac{k\alpha}{2}\cos\left(\frac{k\alpha}{2}\right)\right]}\end{equation}

\[{}\]
%\[{}\]
\section{Fourier Transform of Vector Weight Function $\vec{w}_{1}(r)$:}
\begin{equation}{\vec{w}_1(\vec{r})=w_1(r)\frac{\vec{r}}{r}}\end{equation}
where
\begin{equation}{w_1(r)=\frac{w_2(r)}{4{\pi}r}}\end{equation}
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_1(r)=\frac{1}{4{\pi}\sqrt{\pi}a}\left(\frac{1}{r}\right)e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\[{}\]
%\[{}\]
\section{Fourier Transform of Vector Weight Function $\vec{w}_{2}(r)$:}
\begin{equation}{\vec{w}_2(\vec{r})=w_2(r)\frac{\vec{r}}{r}}\end{equation}
where
\begin{equation}{w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{\frac{\Xi}{\sqrt{2}}}\right)^2}}\end{equation}
temporarily set 
\begin{equation}{a=\frac{\Xi}{\sqrt{2}}}\end{equation}
\begin{equation}{w_2(r)=\frac{1}{a\sqrt{\pi}}e^{-\left(\frac{r-\frac{\alpha}{2}}{a}\right)^2}}\end{equation}

@@

\begin{equation}{\widetilde{\vec{w}}_2(\vec{k})=\frac{-4\sqrt{\pi}i}{ak}\left[\frac{a\alpha\sqrt{\pi}}{2}e^{-\frac{k^2a^2}{4}}\cos\left(\frac{k\alpha}{2}\right)-\frac{a^3k\sqrt{\pi}}{2}e^{-\frac{k^2a^2}{4}}\sin\left(\frac{k\alpha}{2}\right)\right]}\end{equation} 
\begin{displaymath}{+{~~}\frac{4\sqrt{\pi}i}{ak^2}\left[a\sqrt{\pi}e^{-\frac{k^2a^2}{4}}\sin\left(\frac{k\alpha}{2}\right)\right]{~~}\hat{z}'}\end{displaymath}
